Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-13 chi2012.tex
Added qual

\section{Results}
How many native english speakers, only 8 were all enrolled at university all past proficiency test.
\section{Discussion}
What we found

What we didn’t find (evidence for)

What we might look at next -- follow-on work
		We focused on terminological heterogeneity -- didn’t address structural heterogeneity, semantic heterogeneity
		We focused on finite (small) sets Streaming data (how do select future data --) 
		Scale - small data, what are the facilites required for large data
		Collaborative - how might interaction support multiple users collaborating?

Limitations found from study... what is the take away from the limitations
\section{Conclusion} %Key findings of the whole paper and its implications

>>>>

\section{Results}

% behaviours in websites

Users who opted to use websites to make their decisions repeatedly encountered a number of difficulties and issues. In
particular, there was significant confusion over the meaning of data points, for example the percentage-based rankings of
university teaching by the Times Higher Education. There were numerous usability issues in using websites, particularly
in searching for university courses and course requirements. Similarly, participants found it difficult to understand the
locations of restaurants in cities that they were not familiar, and could not find a way to plot the shortlist of restaurants onto
the same map using the websites. Overall, the users that spent the most time using websites exhibited significant
frustration attempting to locate and compare different criteria (such as course entry requirements, or restaurant locations),
and all ended up falling back to using the supplied spreadsheets.

% behaviours in excel
One of the designs of the study was to produce a spreadsheet worksheet for each website, which meant that users
had to switch between the worksheets to gather data from multiple sources. Different approaches to using the spreadsheets
were observed. Some users were keen to collate all data onto a single sheet, so that they could compare the values
all at once. However, this approach was error prone, for example participants noticing too late that the ordering of rows
was different on each sheet, so that their pasted values were incorrectly mapped. Others used pen and paper to collate
the values, which was often faster and resulted in less observed frustration. While the majority of users did not
attempt anything complex with Excel (in fact only one users used charts), there was some advanced use of Excel observed.
One user explained that they did not like to look at numbers, and so coloured the cells of the types of restaurant, and the
friends' preferences, and matched the colours to make their decision. Another user calculated their own weighted metric
of which university to choose by averaging different metrics supplied by the data sources.

% webbox client

The most commonly observed use of WebBox was to collate the data on-screen, and compare multiple values directly.
About half of the observed users actually used the instance combination feature of WebBox, with the other half able
to successfully make decisions without using it. Those who tried to use it were largely successful, and were able
to therefore use the global brush-highlighting to simultaneously compare different statistics. Most users instantly opened
up all data sources into individual boxes, in order to determine which sources contained specific statistics. The result
of this technique is that the users instantly filled their screen, and ran out of space for plots and maps.

%% more from doc here

% weird and wonderful
A number of users admittedly introduced their own bias into the choices: "I prefer Indian food, so I will choose the Indian
restaurant", and one participant spent time on Google Maps looking at the routes to each restaurant, and eliminating
those that required bus transfers (the protocol did not mention routing/transfers at all).

\section{Discussion}

% processes

In order to complete the tasks, the users followed a number of different processes. The most common process followed
was {\it collation} of data, either on-screen or on paper. Some users were proficient enough to copy and paste data
in the supplied spreadsheets from worksheet to worksheet, while others manually typed data value-by-value across worksheets.
Others preferred to collate the data from screen to paper, in order to compare multiple data points. A similar process that
some participants followed was to determine which values of a particular statistic were acceptable, and keep a paper tally
of these next to the set of choices. They then made their choice based on the value of this tally.

Two contrasting approaches that participants followed was to use the data to rule out candidates, or to use the data to
directly compare candidates at once. Our pool of participants exhibited both behaviours evenly, however in the condition
when using the WebBox interface, significantly more comparison (and visualisation of values) was performed, with fewer
participants using the "ruling out" process. A consequence of this was that when asked to justify their choices, users were
able to verify their values on-screen immediately, whereas those who had ruled-out had to memorise their reasons, with
mixed success  -- many participants had to look through the data sources to re-find the reasons why they has ruled out some choices.
Therefore, the uses that were using WebBox were more confident in their choices, and knew exactly why they had chosen them,
often pointing to the screens to show and verify each choice as they explained them.

%What we found 
%
%What we didn’t find (evidence for)
%
%What we might look at next -- follow-on work
%		We focused on terminological heterogeneity -- didn’t address structural heterogeneity, semantic heterogeneity
%		We focused on finite (small) sets Streaming data (how do select future data --) 
%		Scale - small data, what are the facilites required for large data
%		Collaborative - how might interaction support multiple users collaborating?
%
%Limitations found from study... what is the take away from the limitations

\section{Conclusion} %Key findings of the whole paper and its implications
